Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2017-09-26 Paper/Manuscript.tex
Update Manuscript.tex

In this paper, we use a three-country version of \cite{AW2003}'s model for the aggregation of bilateral trade costs and show that there was no difference in nature between the two globalizations.
More generally, we cast doubts on the possibility to distinguish the effect of trade costs and economic expansion through an approach that relies solely on the study of trade flows and excludes \textit{a priori} other possible causes for the evolution of openness rates, like the evolution of vertical specialization and changes in the elasticity of substitution between domestic and foreign goods.
Deducing trade costs from trade flows, and then using trade costs to explain trade flows is essentially a circular reasoning.
Therefore, Jacks \textit{et al.}'s approach cannot be an alternative to traditional investigations of impediments to trade, such as commodity price gaps.

>>>>

In this paper, we use a three-country version of \cite{AW2003}'s model for the aggregation of bilateral trade costs and show that there was no difference in nature between the two globalizations.
More generally, we cast doubts on the possibility to distinguish between the impact of trade costs and the impact of economic expansion through an approach that relies solely on the study of trade flows and excludes \textit{a priori} other possible causes for the evolution of openness rates, like the evolution of vertical specialization and changes in the elasticity of substitution between domestic and foreign goods.
Deducing trade costs from trade flows, and then using trade costs to explain trade flows is essentially a circular reasoning.
Therefore, Jacks \textit{et al.}'s approach cannot be an alternative to traditional investigations of impediments to trade, such as commodity price gaps.
